Funding programmes for early career researchers do/not influence their independence

### 2023-06-09 _targets.Rmd
new updates

  # tarchetypes::tar_download(ids,
  #     urls = Sys.getenv("link_to_supervisors"),
  #     paths = here::here("data", "raw", "supervisors.csv")),
  # tarchetypes::tar_download(gender,
  #     urls = Sys.getenv("link_to_gender"),
  #     paths = here::here("data", "raw", "names4api_tagged.tsv")),
  # tarchetypes::tar_download(authors_arrow,
  #     urls = Sys.getenv("link_to_updated_authors"),
  #     paths = here::here("data", "raw", "authors_by_pubs.arrow")),
  # tarchetypes::tar_download(text_arrow,
  #     urls = Sys.getenv("link_to_updated_texts"),
  #     paths = here::here("data", "raw", "riv_text.arrow")),
  #  tarchetypes::tar_download(sup_control,
  #     urls = Sys.getenv("link_to_supervisors_control"),
  #     paths = here::here("data", "raw", "supervisors_control_final.csv")),

     tar_target(ids_path, here::here("data", "raw", "supervisors.csv"), format = "file"),
     tar_target(ids, read.csv2(ids_path)),
     tar_target(gender_path, here::here("data", "raw", "names4api_tagged.tsv"), format = "file"),
     tar_target(gender, read.delim(gender_path)),
     tar_target(db_path, here::here("data", "raw", "czech_sci_db.sqlite")),
     tar_target(authors_arrow_path, here::here("data", "raw", "authors_by_pubs.arrow")),
     tar_target(authors_arrow, arrow::read_feather(authors_arrow_path)),
     tar_target(text_arrow_path, here::here("data", "raw", "riv_text.arrow")),
     tar_target(text_arrow, arrow::read_feather(text_arrow_path)),
     tar_target(ids_complete, create_ids_complete(ids, db_path)),
     tar_target(ids_complete_vector, make_ids_complete_vector(ids_complete))

@@

      tar_target(matching, match(db_path, ids, gender, authors_arrow)),
      tar_target(sup_path, here::here("data", "raw", "supervisors_control_final.csv"), format = "file"),
      tar_target(sup_control, read.csv2(sup_path)),

>>>>

  tarchetypes::tar_download(ids_path,
      urls = Sys.getenv("link_to_supervisors"),
      paths = here::here("data", "raw", "supervisors.csv")),
  tarchetypes::tar_download(gender_path,
      urls = Sys.getenv("link_to_gender"),
      paths = here::here("data", "raw", "names4api_tagged.tsv")),
  tarchetypes::tar_download(authors_arrow_path,
      urls = Sys.getenv("link_to_updated_authors"),
      paths = here::here("data", "raw", "authors_by_pubs.arrow")),
  tarchetypes::tar_download(text_arrow_path,
      urls = Sys.getenv("link_to_updated_texts"),
      paths = here::here("data", "raw", "riv_text.arrow")),
   tarchetypes::tar_download(sup_path,
      urls = Sys.getenv("link_to_supervisors_control"),
      paths = here::here("data", "raw", "supervisors_control_final.csv")),

     # tar_target(ids_path, here::here("data", "raw", "supervisors.csv"), format = "file"),
     tar_target(ids, read.csv2(ids_path)),
     # tar_target(gender_path, here::here("data", "raw", "names4api_tagged.tsv"), format = "file"),
     tar_target(gender, read.delim(gender_path)),
     tar_target(db_path, here::here("data", "raw", "czech_sci_db.sqlite")),
     # tar_target(authors_arrow_path, here::here("data", "raw", "authors_by_pubs.arrow")),
     tar_target(authors_arrow, arrow::read_feather(authors_arrow_path)),
     # tar_target(text_arrow_path, here::here("data", "raw", "riv_text.arrow")),
     tar_target(text_arrow, arrow::read_feather(text_arrow_path)),
     tar_target(ids_complete, create_ids_complete(ids, db_path)),
     tar_target(ids_complete_vector, make_ids_complete_vector(ids_complete))

@@

      tar_target(matching, match(db_path, ids, gender, authors_arrow)),
      # tar_target(sup_path, here::here("data", "raw", "supervisors_control_final.csv"), format = "file"),
      tar_target(sup_control, read.csv2(sup_path)),

### 2023-06-09 article.Rmd
new updates

all <- r_before_final %>% filter(vedidk %in% a)

@@

>>>>

all <- rbind(r_before_final, r_after_final) %>% filter(vedidk %in% a)

@@

### Before intervention

```{r echo=FALSE}

# assuming df is your dataframe
df <- r_before_final

# list of numeric columns. Exclude treatment column
numeric_vars <- df %>% select(where(is.numeric)) %>% names()

# descriptive stats for treatment level 0
desc_0 <- df %>%
  filter(treatment == 0) %>%
  summarise(across(all_of(numeric_vars), list(mean = mean, sd = sd, min = min, max = max)))

# descriptive stats for treatment level 1
desc_1 <- df %>%
  filter(treatment == 1) %>%
  summarise(across(all_of(numeric_vars), list(mean = mean, sd = sd, min = min, max = max)))

# descriptive stats for treatment level 2
desc_2 <- df %>%
  filter(treatment == 2) %>%
  summarise(across(all_of(numeric_vars), list(mean = mean, sd = sd, min = min, max = max)))

# Now you can print these as tables in your Rmd document

# Print table for treatment level 0
kable(desc_0, caption = "Descriptive statistics for treatment level 0")

# Print table for treatment level 1
kable(desc_1, caption = "Descriptive statistics for treatment level 1")

# Print table for treatment level 2
kable(desc_2, caption = "Descriptive statistics for treatment level 2")

### After intervention

```{r echo=FALSE}
d <- tar_read(full_indicator)
na_counts <- sum(is.na(d$RII))
